Is essentiality of genes conserved in Enterobacteriaceae?

### 2016-09-19 documents/manuscript.tex
Added word enrichment analysis figure for beneficial losses

We have divided the clusters of orthologous genes into 4 groups based on their essentiality (essential, ambiguous, non-essential, and beneficial loss) and 3 groups based on their conservation (genus specific, single copy, and multi-copy). The results are depicted in Fig.\@ \ref{fig:iidist}. The figure shows that most of the essential clusters are single copy and most of the beneficial losses are genus specific. \textcolor{red}{\{KEGG results\}}
\subsection{Evolution of essentiality}
We have compared the number of genes that are conserved in different strains in our study and the number of genes that are essential in these strains. The results propose that although conservation of genes follows a tree-like trend, the essentiality does not show a tree-like signal.
\begin{itemize}
\item UpSetR results (Fig.~\ref{fig:upsetr})
\item Stringent
\item Dollo law
\item Ancestral insertion index
\end{itemize}
\section{Case study of genes}
\subsection{Core genes}
\subsection{Accessory genes}

@@

>>>>

We have divided the clusters of orthologous genes into 4 groups based on their essentiality (essential, ambiguous, non-essential, and beneficial loss) and 3 groups based on their conservation (genus specific, single copy, and multi-copy). The results are depicted in Fig.\@ \ref{fig:iidist}. The figure shows that most of the essential clusters are single copy and most of the beneficial losses are genus specific.

\textcolor{red}{\{KEGG results\}} We have done a word enrichment analysis on the description of the beneficial losses in Fig.\@ \ref{fig:essentiality-pval}. It shows that most of the beneficial losses are mobile elements. Most of these mobile elements are not included in KEGG database.
\subsection{Evolution of essentiality}
We have compared the number of genes that are conserved in different strains in our study and the number of genes that are essential in these strains. The results propose that although conservation of genes follows a tree-like trend, the essentiality does not show a tree-like signal.
\begin{itemize}
\item UpSetR results (Fig.~\ref{fig:upsetr})
\item Stringent
\item Dollo law
\item Ancestral insertion index
\end{itemize}
\section{Case study of genes}
\subsection{Core genes}
\subsection{Accessory genes}

@@

\begin{figure}
\includegraphics[scale=0.7]{essentiality-pval.pdf}
\caption{The word enrichment analysis for beneficial losses compared to other genes. The red line shows p-value = 0.05.}
\label{fig:essentiality-pval}
\end{figure}
